---
title: "Présentation R"
author: "Arthur Lemoine, François Someville, Alexandre Antippas"
date: "Janvier 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
chooseCRANmirror(graphics=FALSE, ind=1)
pkgs <- c("ggplot2","dplyr","lubridate","ade4","tm","SnowballC","wordcloud","cluster","factoextra","NbClust")
install.packages(pkgs)
library(dplyr)
library(ggplot2)
library(data.table)
library(lubridate)
library(ade4)
library(tm)
library(SnowballC)
library(wordcloud)
library(cluster)
library(factoextra)
library(NbClust)
```

```{r load myData, include=FALSE}
load("data.RData")
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

```{r}

```


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
